\textbf{NBA Party}

### 2017-07-03 cardinal_analytx_presentation/nightlife_and_sports.tex
Added previous research section alongside citations.

  \begin{block}{Previous research}
    Players under-perform proportion of shots made on Sundays.\footnote{Chase ('15): 1,092 NBA players under-perform relative to their own season-long average out of 2,035 who took at least one shot on Sunday.}

    Teams under-perform bookmakers expectations on Sunday afternoons when on the road.\footnote{Ezekowitz, ('14): Only 129 out of 284 games did the away team meet the spread, using 2008-14 data.}   \end{block}

@@

@@

\begin{frame}
  \frametitle{How can we measure unexpected changes in performance?}     \begin{block}{Bookmaker spreads}     
    The expected score differential between two teams.

@@

    A team is expected to meet the spread $\frac{1}{2}$ the time.\footnote{Dubner and Levitt, 2006}
  \end{block}
  \begin{block}{Bookmaker money-lines}     The odds that a team will beat their opponent.

@@

    Weaker, still: if odds of beating the spread uncorrelated \\
    $\leadsto$ identification.\footnote{Under an efficient market, the latter assumption should hold.}    \end{block}  
\end{frame}

>>>>

@@

\begin{frame}
  \frametitle{Previous Research - Player shooting average}     Players under-perform proportion of shots made on Sundays.\footnote{Chase, ('15).}
    \begin{itemize}       \item 1,092 of 2,035 NBA players who took $\geq 1$ shot on Sundays under-perform relative to their own season-long average; $p=0.001$.
      \item Effect size is not considered.
      \item Density of support is questionable.\footnote{What if we miss the only shot we took on Sunday, should that be considered?}     \end{itemize}
\end{frame}

\begin{frame}   \frametitle{Previous Research - Team's ability to meet spread}
  Teams under-perform bookmakers expectations on Sunday afternoons when on the road.\footnote{Ezekowitz, ('14).}
    \begin{itemize}       
    \item Only 129 out of 284 games did the away team meet the spread, 
      using 2008-14 data; $p=0.1089$.
    \item Not quite significant at the 90\% confidence level.     
    \end{itemize}
  \end{frame}

@@

\begin{frame}
  \frametitle{How can we measure unexpected changes in performance?}     \begin{block}{Bookmaker spreads (NBA)}     
    The expected score differential between two teams.

@@

    A team is expected to meet the spread $\frac{1}{2}$ the time.\footnote{Dubner and Levitt, 2006}
  \end{block}
  \begin{block}{Bookmaker money-lines (MLB)}     The odds that a team will beat their opponent.

@@

    Weaker, still: if odds of beating the spread uncorrelated \\
    $\leadsto$ identification.\footnote{Under an efficient market, this assumption should hold.}    \end{block}  
\end{frame}
